Effect of quality-adjusted production function inputs

### 2015-07-08 Articles/Article_EcolEcon_2015/EcolEcon_2015.Rnw
Rearranging the articles.

In this paper, we assess two prominent energy-augmented production functions 
that appear in the literature: 
Cobb-Douglas (CD) and
Constant Elasticity of Substitution (CES).
The following subsections describe each.

@@

@@

myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="kle")) %>% 

@@

myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="lek")) %>% 

@@

myXTable(filter(AllCoeffs, model=="CES" & (nest=="kl" | nest=="ekl")) %>% 

@@

  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=cst)) +

@@

  scale_shape_manual(values=c(1, 16)) + 

@@

  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, shape=cst)) +

@@

#   scale_x_continuous(breaks=seq(-0.005, 0, 0.005)) +  

@@

<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=

@@

  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
             mapping=aes(x=Dmse, y=Dlambda, color=energy, shape=nest)) +
  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
             mapping=aes(x=Dmse, y=Dlambda, color=energy), shape=1) +

@@

<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse$) for the CES modles relative to the Unadjusted, Without energy, CST case.">>=

@@

  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Reject CST"), 
             mapping=aes(x=Dmse, y=percDlambda, color=energy, shape=nest)) +
  geom_point(data=filter(AllCoeffs, model=="CES" & cst=="Adhere to CST"), 
             mapping=aes(x=Dmse, y=percDlambda, color=energy), shape=1) + 

@@

@@

  scale_y_continuous(breaks=seq(-75, 25, 25)) +  

>>>>

In this paper, we assess two prominent energy-augmented production functions 
that appear in the literature: 
Cobb-Douglas (CD) and
Constant Elasticity of Substitution (CES).
These production functions are assessed relative to 
a model of exponential growth only.
The following subsections describe each.

@@

%------------------------------
\subsubsection{Exponential Production Function} 
\label{sec:exp}
%------------------------------

We define an exponential-only reference model for economic growth
in Equation~\ref{eq:exponential-only-model}.
%
\begin{equation} \label{eq:exponential-only-model}
  y = \theta A \; ; \; A \equiv \mathrm{e}^{\lambda(t-t_0)} \; .
\end{equation}
%
The reference model is a degenerate case of the Cobb-Douglas production function
wherein all factor shares are zero~($\alpha_1 = \alpha_2 = \alpha_3 = 0$)
and the constant returns to scale constraint is not respected.

We expect that the reference model will have a larger fitted Solow residual term than
the Cobb-Douglas and CES models, because no factors of production are
included in the reference model to drive growth.
Indeed, in the reference model, 
all growth is attributed to the Solow residual.

In contrast, it is not necessarily true that 
Cobb-Douglas and CES models 
will exhibit lower $mse$ than the reference model
shown in Equation~\ref{eq:exponential-only-model}.
The Cobb-Douglas and CES models have more fitting parameters,
but they incorporate the factors of production
at constant returns to scale. 
The reference model has $\alpha_1 + \alpha_2 + \alpha_3 = 0$,
whereas our implementations of both the Cobb-Douglas and CES models
requires constant returns to scale, $\alpha_1 + \alpha_2 + \alpha_3 = 1$.
Thus, if the factors of production ($\alpha_1$, $\alpha_2$, and $\alpha_3$) 
are poorly correlated to output ($y$),
the constant returns to scale constraint may cause higher $mse$ for
the Cobb-Douglas or CES models relative to the reference model.

In the sections that follow, 
we assess the Cobb-Douglas and CES models relative to the reference model
in terms of goodness of both goodness of fit~($mse$) and Solow residual~($\lambda$).

@@

myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="kle")) | model=="exp") %>% 

@@

myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="lek")) | model=="exp") %>% 

@@

myXTable(filter(AllCoeffs, (model=="CES" & (nest=="kl" | nest=="ekl")) | model=="exp") %>% 

@@

  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst)) +

@@

  scale_size_manual(values=c(2,3.5)) +

@@

  geom_point(data=filter(AllCoeffs, model=="CD"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst)) +

@@

  scale_x_continuous(breaks=seq(-50, 50, 50), limits=c(-90, 50)) +  

@@

<<DSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Change in Solow Residuals~($\\Delta\\lambda$) and mean squared error~($\\Delta mse$) for the CES modles relative to the exponential-only model.">>=

@@

  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=Dmse, y=Dlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +

@@

<<percDSRmse_CES_graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Percentage change in Solow Residuals~($\\Delta\\lambda \\, [\\%]$) and mean squared error~($\\Delta mse \\, [\\%]$) for the CES models relative to the exponential-only model.">>=

@@

  geom_point(data=filter(AllCoeffs, model=="CES"), mapping=aes(x=percDmse, y=percDlambda, color=energy, size=cst, shape=nest)) +
  scale_size_manual(values=c(2,3.5)) +
  scale_shape_manual(values=c(16,17,18,15)) +

@@

  scale_x_continuous(breaks=seq(-80, 0, 20)) +  

@@
